Democractic Algorithm: A Novel Approach to Hierarchical Swarm Intelligence\\

### 2020-09-25 VLSID/paper.tex
26_09_report_1

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{amsmath}% http://ctan.org/pkg/amsmath
\newcommand\sufr[3][0pt]{$\rule{0pt}{\dimexpr#1+1.4ex\relax}^\frac{#2}{#3}$}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

Based on the mathematical representation, the following observations can be made:
\begin{itemize}
\item The updation process occurs at an individual and departmental level to save the best solutions obtained so far
\item The parameters $\vec{A}$ and $\vec{C}$ assist the solutions to have higher dimensionality
\item Due to the dual updation and introduction of a memory element, the problems functions will saturate at a middle level department
\item The voting season provides weighted rights to each candidate in each department. The weights are assigned based on the individual's fitness which in turn is dependent on their department's position 
\item The increased number of parameters requires fine tunning which can be automated
\end{itemize}

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsmath,amsfonts}
\usepackage{array,booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{stackrel}
\usepackage{breqn}
% \usepackage{isomath}
\usepackage{mathtools}
% http://ctan.org/pkg/amsmath
\newcommand\sufr[3][0pt]{$\rule{0pt}{\dimexpr#1+1.4ex\relax}^\frac{#2}{#3}$}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

Based on the mathematical representation, the following observations can be made:
\begin{itemize}
\item The updation process occurs at an individual and departmental level to save the best solutions obtained so far
\item The parameters $\vec{A}$ and $\vec{C}$ assist the solutions to have higher dimensionality
\item Due to the dual updation and introduction of a memory element, the problems functions will saturate at a middle level department
\item The voting season provides weighted rights to each candidate in each department. The weights are assigned based on the individual's fitness which in turn is dependent on their department's position 
\item As the department rank increases, the number of individual candidate in the department decreases to promote elitism. This would ensure survival of the best solutions in future problems. 
\item As the department rank decreases, the number of individual candidate in the department increase to promote diversity. This would open up new avenues to explore and possibly increase chances of finding the gobal optimum.  
\item The increased number of parameters requires fine tunning which can be automated
\end{itemize}

@@

\section{Results and Discussion}

In this section the DA algorithm is benchmarked against 18 standard minimization functions. These functions are described in Table $\ref{tab:1}$. The DA was iterated 20 times on each of these functions and the results were compared against other popular SI algorithms such as Particle Swarm Optimization (PSO), Grey Wolf Optimization (GWO), Multiverse Optimization (MVO) and Cuckoo Search (CS). The metric based results such as mean and standard deviation is listed in Table

\begin{table*}[!t]
\caption{\textsc{Benchmark Functions}}
\label{tab:1}
\centering
\scalebox{0.9}
{
\begin{tabular}{| >{\arraybackslash}m{0.88in} | c | c | >{\arraybackslash}m{0.4in} | c | >{\arraybackslash}m{1in} |}
\hline
Function & ID & Formula & Modality & Range & Minimum Value \\
\hline
Matyas & F1 & $0.26(x\textsubscript{2} + y\textsubscript{2}) - 0.48xy$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Booth & F2 & $(x + 2y - 7)\textsuperscript{2} + (2x + y - 5)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,3)\\
Bohachevsky & F3 & $x\textsuperscript{2} + 2y\textsuperscript{2} -0.3cos(3\pi x)-0.4cos(4\pi y)+0.7$ & Uni & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Gramacy and Lee & F4 & $\frac{sin(10\pi x)}{2x} + (x-1)\textsuperscript{4}$ & Uni & [-0.5,2.5] & -0.869011134989500 at $x\textsuperscript{*}$ = (0.548563444114526)\\
Leon & F5 & $100(y-x\textsuperscript{3})\textsuperscript{2}$ + $(1-x)\textsuperscript{2}$ & Uni & [-10,10] & 0 at $x\textsuperscript{*}$ = (1,1)\\
Ackley & F6 & $-20 exp(-0.2 \sqrt{\frac{1}{n} \sum_{i=1}^n x_i^2}) - exp(\frac{1}{n} \sum_{i=1}^n cos(2\pi x_i)) + 20 + e$ & Multi & [-32,32] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Bartels & F7 & $|x\textsuperscript{2} + y\textsuperscript{2} + xy| + |sin(x)| + |cos(y)|$ & Multi & [-500,500], [-500,500] & 1 at $x\textsuperscript{*}$ = (0,0)\\
Branin & F8 & $a(x\textsubscript{2} - bx\textsubscript{1}\textsuperscript{2} + cx\textsubscript{1} - r)\textsuperscript{2}$ + $s(1-t)cos(x\textsubscript{1})$ + s & Multi & [-5,10], [0,15] & 0.397887 at $x\textsuperscript{*}$ = (-$\pi$, 12.2.275)\\
Egg Crate & F9 & $x\textsuperscript{2}$ + $y\textsuperscript{2}$ + $25(sin\textsuperscript{2}(x) + cos\textsuperscript{2}(x))$ & Multi & [-5,5] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Qing & F10 & $\sum_{i=1}^{n}(x^2-i)^2$ & Multi & [-500,500] & 0 at $x\textsuperscript{*}$ = ($\pm\sqrt{i}$)\\
Rastrigin & F11 & $10n + \sum_{i=1}^{n}(x_i^2 - 10cos(2\pi x_i))$ & Multi & [-5.12,5.12], [-500,500] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Rosenbrock & F12 & $\sum_{i=1}^{n}[b (x_{i+1} - x_i^2)^ 2 + (a - x_i)^2]$ & Multi & [-5.12,5.12], [-5,10] & 0 at $x\textsuperscript{*}$ = (1)\\
Bird & F13 & $sin(x)e\textsuperscript{(1-cos(y))^2}+cos(y)e\textsuperscript{(1-sin(x))^2}+(x-y)\textsubscript{2}$ & Multi & [-2$\pi$, 2$\pi$] & -106.764537 at $x\textsuperscript{*}$ = (4.70104,3.15294), (-1.58214,-3.13024)\\
Powell Sum & F14 & $\sum_{i=1}^{n}|x_i|^{i+1}$ & Multi & [-1,1] & 0 at $x\textsuperscript{*}$ = 0\\
Schaffer & F15 & $0.5 + \frac{sin\textsuperscript{2}(x\textsuperscript{2}-y\textsuperscript{2})-0.5}{(1+0.001(x\textsuperscript{2}+x\textsuperscript{2}))\textsuperscript{2}}$ & Multi & [-100,100] & 0 at $x\textsuperscript{*}$ = (0,0)\\
Shubert & F16 & $\prod_{i=1}^{n}{\left(\sum_{j=1}^5{ cos((j+1)x_i+j)}\right)}$ & Multi & [-10,10] & -186.7309 \\
Happy Cat & F17 & $\left[\left(||\textbf{x}||^2 - n\right)^2\right]^\alpha + \frac{1}{n}\left(\frac{1}{2}||\textbf{x}||^2+\sum_{i=1}^{n}x_i\right)+\frac{1}{2}$ & Multi & [-2,2] & 0 at $x\textsuperscript{*}$ = (-1) \\
Alpine & F18 & $\prod_{i=1}^{n}\sqrt{x_i}sin(x_i)$ & Multi & [0,10] & 2.808 at $x\textsuperscript{*}$ = (7.917) \\
\hline
\end{tabular}
}
\end{table*}

\begin{table*}[t]
\caption{\textsc{Benchmark Results}}
\label{tab:2}
\centering
{
\begin{tabular}{| c | c  c | c  c | c  c | c  c | c  c |}
\hline
{\textbf{Function}}&{\textbf{PSO}}&{}&{\textbf{GWO}}&{}&{\textbf{MVO}}&{}&{\textbf{CS}}&{}&{\textbf{DA}}&{}\\
\hline
{}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}&{\textbf{Mean}}&{\textbf{Std}}\\
\hline
{F1}&{1.39E-08}&{6.24E-04}&{2.41E-06}&{4.98E-05}&{5.21E-06}&{8.23E-08}&{9.11E-06}&{4.39E-07}&{8.71E-06}&{5.11E-05}\\
{F2}&{4.89E-10}&{8.79E-04}&{6.76E-09}&{5.11E-06}&{6.18E-07}&{5.84E-08}&{9.51E-09}&{3.84E-07}&{7.62E-11}&{2.62E-06}\\
{F3}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F4}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F5}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F6}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F7}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F8}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F9}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F10}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F11}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F12}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F13}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F14}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F15}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F16}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F17}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
{F18}&{}&{}&{}&{}&{}&{}&{}&{}&{}&{}\\
\hline
\end{tabular}
}
\end{table*}
